%\chapter{\leavevmode}
\chapter{\leavevmode Proposed Research}
% \chapter*{Proposed Research}
% \addcontentsline{toc}{chapter}{Proposed Research}
\label{chap:proposedresearch}


% Research Objectives
% The goal of the research is to get an idea of what the potential "threat map" looks like.
% With the technical "specs" for the hardware and OS, can we manipulate device capabilities?
% What capabilities can we extend or add?

% \section*{Research Objectives }
% \addcontentsline{toc}{section}{Research Objectives}
\section{Research Objectives }

The goal of this research is to understand the hardware and software capabilities of serial print devices. Whether the hardware can support adding unintended functionality at the application and physical layers. And, with what we know about the USB standard and developing real time operating systems, can that functionality be used to create a dual purpose device?


% \section*{Research Questions/Hypotheses}
% \addcontentsline{toc}{section}{Research Questions/Hypotheses}
\section{Research Questions}

The research questions this study aims to answer are as follows:

\begin{itemize}
  \item \textbf{RQ1:} What is the baseline or minimum hardware these devices are running?
  \item \textbf{RQ2:} What software is being used on these devices? OS, libraries...
  \item \textbf{RQ3:} Can the software/firmware be modified? FreeRTOS/ReconOS/VXWorks.
  \item \textbf{RQ4:} If so, how much can be modified in memory? Is manually reflashing possible?
  \item \textbf{RQ5:} Assuming reflashing is possible, can the original OS keep original functions and be used as a HID clone or hub?
\end{itemize}


% \section*{Methodology}
% \addcontentsline{toc}{section}{Methodology}
\section{Methodology}
Likely, but not limited to the following:
\begin{itemize}
  \item Gather recent research within the last 5-10 years for manufacturer/device shares of the market
  \item Gather technical sheets and specs for the most popular devices
  \item Take note of the hardware specs for each device as well as firmware used
  \item Create default/debug images of each popular devices' firmware - what is natively supported?
  \item Is there room to add functionality without crippling original function
\end{itemize}


\subsection{Design Science}



\subsection{Design Science}



\subsection{Reporting}

