
%%% Introduction

Overview Outline:
\begin{itemize}
  \item Discuss why we are looking into serial printer devices
  \item Explain what platforms there are
  \item What are the current threats
  \item What will this information be used for?
  \item State the research questions and goals
\end{itemize}

Background Outline:
\begin{itemize}
  \item Further background on specific devices, manufacturers, platforms, and architectures
  \item Do these devices get hijacked often? Explain it: how, when, by what...
  \item Statistics on point-of-sale (PoS) systems involved in financial cybercrime
  \item Where are the majority of cybercrimes committed
  \item How does this involve serial printer devices?
  \item Maybe, include background info on the platforms (FreeRTOS/RTOS/Yocto)
  \item Introduce common methods used for researching these devices
\end{itemize}

%%% Literature Review

Paper Review Outline:
\begin{itemize}
  \item None of the papers to be used for this proposal have been decided yet.
  \item Once that has been decided, each paper will have it's own section/subsection.
  \item And, the papers will be reviewed based on their contributions.
  \item This section will also be useful for establishing what is current.
\end{itemize}

Summary Outline:
\begin{itemize}
  \item None of the papers to be used for this proposal have been decided yet.
  \item Once that has been decided, each paper will have it's own section/subsection.
  \item And, the papers will be reviewed based on their contributions.
  \item This section will also be useful for establishing what is current.
\end{itemize}

%%% Proposed Research

Research Objectives Outline:
\begin{itemize}
  \item The goal of the research is to get an idea of what the potential "threat map" looks like.
  \item With the technical "specs" for the hardware and OS, can we manipulate device capabilities?
  \item What capabilities can we extend or add?
\end{itemize}

Research Questions/Hypotheses Outline:
\begin{itemize}
  \item What is the baseline or minimum hardware these devices are running?
  \item What software is being used on these devices? OS, libraries...
  \item Can the software/firmware be modified?
  \item If so, how much can be modified? In memory? Reflashed?
  \item Given hardware baseline, what does that performance support? Intended functions plus a webserver?
\end{itemize}

Methodology, likely, but not limited to the following:
\begin{itemize}
  \item Gather recent research within the last 5-10 years for manufacturer/device shares of the market
  \item Gather technical sheets and specs for the most popular devices
  \item Take note of the hardware specs for each device as well as firmware used
  \item Create default/debug images of each popular devices' firmware - what is natively supported?
  \item Is there room to add functionality without crippling original function
\end{itemize}

%%% Timeline

Timeline Outline:
\begin{itemize}
  \item Formal timeline broken down by months or quarters
  \item Provide expected actions and deliverables for each deadline
  \item Likely, Gantt chart with "Agile" mindset
\end{itemize}

%%% Conclusion

Conclusion Outline:
\begin{itemize}
  \item Restate the research objectives, questions, what the research topic is and how this research will answer them.
  \item Briefly mention significance/impact in relation to the topic.
  \item Thank readers.
\end{itemize}